---
title: "simpleRegress"
author: "Alex Moreno"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

Plot is positive linear. Median of -0.0822, Minimum of -11.12, and Max of 20.93

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

```{r}
chesty <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(chesty)
summary.lm(chesty)
```

The adjusted R-square for this model (CHESTY) is 0.79, the model for NECK had an adjusted R-square of 0.75.
So far the best model is the one based on the CHEST.

```{r}
new <- data.frame(CHEST=c(17,22,26))
predict(chesty,new)
predict(chesty,new,se.fit=TRUE)
```


```{r}
weighty <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(weighty)
summary.lm(weighty)
```

Weight as the comparison seems to be similar producing the same p-value. The standard error is larger though. 



##  Conclusion

The best option from analyzing the plots is to use length with chest. It has the least value in error and gives more accurate results. The test used were numerical vs numerical since thee values are all numerical. The subject was bears and analyziong the length, weight, neck and chest sizes. If sex was an option that would be a categorical value. 
